% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\usepackage{hyperref}
\usepackage{color}
\begin{document}
\name{Yeow-Khiang Chia}

\address{ %centerline{Institute for Infocomm Research, Singapore} \\
%\centerline{1 Fusionopolis Way, \#21-01 Connexis (South Tower)} \\
%\centerline{Singapore 138632} \\
\centerline{\textbf{Telephone}: +65 97905564} \\
\centerline{\textbf{Email}: \href{mailto:yeowkhiang@gmail.com}{yeowkhiang@gmail.com}} \\
\centerline{\textbf{Website}: \url{http://ykchia.github.io/}} 
}                                 
                        
\begin{resume}            
 
%\section{Objective}    Obtain a Quantitative Researcher or Data Scientist position in Finance, with emphasis on applications of machine learning and signal processing to Quantitative Finance

\section{Research \hspace{1pt} Interests}  
Information Theory, Machine Learning, Statistical Signal Processing, Mathematical Optimization, Data Analytics

\section{Education}       \textbf{Stanford University} \\
Ph.D. in Electrical Engineering, January 2012 \\
Thesis topic: Multi-terminal Secrecy and Source Coding \\
GPA: 4.0/4.0 \\
Advisers: Profs. Abbas El Gamal and Tsachy Weissman \\
Thesis Committee: Profs. Thomas Cover and Ada Poon

 \textbf{Stanford University}\\
M.S. in Electrical Engineering, January 2012, GPA: 4.0/4.0 

 \textbf{Imperial College, London} \\
M.Eng. (First Class Honours) in Electrical Engineering June 2001\\
Thesis topic: Lyapunov methods for adaptive gain control

\section{Professional Experience}
Research Staff Member, \textbf{IBM Research Singapore}. June 2015 - Current
\begin{itemize}
\item Principal investigator for project between Maritime and Port Authority of Singapore (MPA) and IBM in developing a sense-making and predictive analytics system for MPA. Project involves using data analytics and machine learning to enhance MPA's operations in the Maritime domain
\item Research on data analytics and signal processing for road networks. Co-developed an adaptive sampling algorithm for efficient collection, and accurate estimation, of traffic information in road networks. Patent filed in the United States 
\end{itemize}
Scientist II, \textbf{Data Analytics Department, Institute for Infocomm Research, Singapore} \\
April 2014 - May 2015. Worked on the following projects
\begin{itemize}
\item Financial and Audit Analytics for DBS Singapore. Project is part of DBS-I2R Joint laboratory.
\item Financial Analytics and Algorithms for commodity trading. Project is a joint project with Wealth Sciences Pte Ltd and Straits Financial LLC.
\item Signal processing algorithms for Book Sequencing from RFID time series readings. Joint project with National Library Board of Singapore.
\end{itemize}

Scientist I, \textbf{Advanced Communication Department, Institute for Infocomm Research, Singapore}. Feb 2012 - April 2014. \\
Worked on the following projects: i) Energy resource optimization in cellular networks with renewable energy resources; ii) Fundamental Information Theoretic limits of network communication systems.

Research Assistant, \textbf{El Gamal Research Group, Stanford University}\\
September 2006 - December 2011. PhD thesis research on Network Information Theory

Visiting Research student, Prof. Zhang Lin's group, \textbf{Tsinghua University, China}\\
March 2010 - May 2010. Worked on Throughout and Delay scaling in wireless mobile networks

Summer Intern, \textbf{Ji Research Group,Stanford University}\\
June 2007- September 2007. Worked with Profs. Hanlee Ji and Tsachy Weissman on signal processing for shotgun DNA sequencing

Research Engineer at \textbf{Institute for Infocomm Research, Singapore} \\
August 2005 - August 2006. Worked with on signal processing for localization

Strategic Planning Executive, \textbf{Ministry of Home Affairs, Singapore} \\
April 2003 - July 2005. Responsible for Manpower, Budget and planning policies.

%\item Special projects clerk, Operations Research Department, G5 Army, Singapore. \\
%June 2002 - April 2003.
Summer intern at \textbf{Center for Imaging, Remote Sensing and Processing (CRISP)} \\
July 2000 - September 2000. Worked on image processing algorithms for satellite images


%\item Special projects clerk, Operations Research Department, G5 Army, Singapore. \\
%June 2002 - April 2003.
Summer intern at \textbf{Center for Imaging, Remote Sensing and Processing (CRISP)} \\
July 2000 - September 2000. Worked on image processing algorithms for satellite images

\section{Awards and Honors}
Institute of Engineers Singapore (IES) Prestigious Engineering Achievement Award 2015 for project ``The Future of Audit: Predictive Analytics on Irregularities and Risks in Bank Branches''. Joint project between Institute for Infocomm Research and DBS Bank

IEEE Transactions on Communications Exemplary Reviewer 2016

Stanford Graduate Fellowship, 2009 - 2011

Singapore Agency for Science, Technology and Research (A*STAR) National Science Scholarship, 2006-2011

IEE prize for distinction (best all round student) in the four years degree course at Department of Electrical and Electronics Engineering, Imperial College. June 2001 

Singapore Public Service Commission scholarship for undergraduate studies at Imperial College, 1997-2001

\section{Skills}
Please see the long version for a full list of Masters and PhD level courses taken at Stanford University, as well as online courses taken with Coursera, edX and Udacity. Courses cover the following areas
\begin{itemize}
\item Information Theory and Probability Theory
\item Machine Learning, including Deep Learning, Big Data Analysis with Apache Spark, and Managing Big Data with MySQL
\item Signal Processing and Digital Communications
\item Mathematical Optimization and Discrete Algorithms
\item Control Theory, Linear Dynamical Systems and Stochastic Systems
\item Game Theory and Economics
\end{itemize}
\iffalse
\textbf{Masters and PhD level courses} taken at Stanford University: \textbf{Information Theory, Probability Theory and Stochastic Systems}; \textbf{Machine Learning and Signal Processing}; \textbf{Mathematical Optimization and Discrete Algorithms}; \textbf{Control Theory, Game Theory and Economics}. 

\textbf{Online courses:} I have also taken and completed the following online courses: \textbf{Machine Learning (Coursera), May 2014}, \textbf{Introduction to Statistical Learning with R (Stanford Online), April 2014}.

A full list of courses taken is given in \textbf{Appendix A}
\fi
Programming skills and experience: Proficient in \textbf{Python}, \textbf{R}, \textbf{Java}, \textbf{C++}, \textbf{Matlab} 

\section{Publications and Patents}
1 patent filed in the United States and 36 publications in top IEEE journals and conferences. A full list of patents and publications is given in the long version, or the following website:
\url{http://ykchia.github.io/publications.html}

\section{Teaching Experience}
Teaching assistant for courses on Signal Processing (2011, Instructor: Prof. Tsachy Weissman) and Information Theory (2010, Instructor: Prof. Abbas El Gamal)
\iffalse
\begin{itemize}
\item Introduction to Statistical Signal Processing. Instructor: Prof. Tsachy Weissman, 2012
\item Short course in Network Information Theory taught at Tsinghua University, China. Instructor: Prof. Abbas El Gamal, 2010
\end{itemize}
\fi
\iffalse
Teaching Assistant, EE278A: Introduction to Statistical Signal Processing \\
Taught by Prof. Tsachy Weissman, Fall 2012. 

Teaching Assistant for 
\fi

%A full list of publications can be obtained from the following website: \\
%\url{http://www1.i2r.a-star.edu.sg/~chiayk/publications.html}

\section{Professional Activities}
Reviewer since 2009 for the IEEE journals and conferences: Information Theory, Communications, Wireless Communications, Information Security and Forensics
\iffalse
\begin{itemize}
\item IEEE Transactions on Information Theory 2009 - Current
\item IEEE Symposium on Information Theory 2009- Current 
\item Other IEEE Transactions: Communications, Wireless Communications, Information Security and Forensics 
\end{itemize}
\fi
%Member, IEEE and IEEE Information Theory Society
\iffalse
\section{Community Service}
Military Service in the Singapore Army 2001 - 2003. %Served as a special projects clerk in the Operations Research Department of the Singapore Army
\fi
\iffalse
\section{References} 
%Available on request
%\iffalse
Available on request.
\fi
\iffalse
\begin{table}[ht]
\begin{tabular}{l l}
Prof. Abbas El Gamal & Prof. Tsachy Weissman \\ 
Stanford University & Stanford University \\
Dept. of Electrical Engineering & Dept. of Electrical Engineering \\
&  \\
Prof. Haim Permuter & Dr Rajiv Soundararajan \\
Ben Gurion University & Qualcomm Research India \\
Dept. of Elec. and Com. Engineering & 
\end{tabular}
\end{table}
\fi
%\fi
\end{resume} 

\end{document}









